A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
Footnotes and final reference
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@970 43ef1190-90fd-4dd7-a769-d0121f02b80e

To compile a list of Web ontologies, we first queried the Linked Open
Vocabularies (LOV) \cite{doi:10.1108/LHT-03-2013-0027} SPARQL endpoint
to retrieve all registered ontologies. Then, we took the full list of
URIs registered with prefix.cc. The assumption that they all identify
an ontology is clearly false, as we found that for example Tim
Berners-Lee's FOAF profile has a registered URI, but it is unlikely to
introduce significant bias.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity,stat1,specs}

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011} was used
to parse the line. Lines that failed to parse was discarded. We have
not investigated whether this could introduce biases. Statements were
then accepted into a new NQuad file if they had a predicate that
matched the
\rdfterm{sd:endpoint}\footnote{http://www.w3.org/TR/sparql11-service-description/#sd-endpoint}
or matched a case-insensitive regular expression \texttt{sparql} if
the subject and objects were both resources, or the predicates
\rdfterm{void:vocabulary}\footnote{http://www.w3.org/TR/void/#vocabularies},
\rdfterm{rdfa:vocabulary}\footnote{http://www.w3.org/TR/rdfa-core/#term-prefix-definitions-vocabulary}
or
\rdfterm{api:vocabulary}\footnote{http://purl.org/linked-data/api/vocab#vocabulary},
as well as having an resource as object. Finally, statements with the
the classes
\rdfterm{cogs:Endpoint}\footnote{http://vocab.deri.ie/cogs#Endpoint},
\rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary}\footnote{http://lov.okfn.org/vocab/voaf/v2.3/index.html#Vocabulary}
in the object position were also accepted. More classes and properties
were considered, but not used in the data reduction if they did not
occur in the original data.

>>>>

To compile a list of Web ontologies, we first queried the Linked Open
Vocabularies (LOV) \cite{lov2} SPARQL endpoint
to retrieve all registered ontologies. Then, we took the full list of
URIs registered with prefix.cc. The assumption that they all identify
an ontology is clearly false, as we found that for example Tim
Berners-Lee's FOAF profile has a registered URI, but it is unlikely to
introduce significant bias.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs}

@@

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework
RDF::Trine\footnote{https://metacpan.org/release/GWILLIAMS/RDF-Trine-1.011} was used
to parse the line. Lines that failed to parse was discarded. We have
not investigated whether this could introduce biases. Statements were
then accepted into a new NQuad file if they had a predicate that
matched the
\rdfterm{sd:endpoint}\footnote{http://www.w3.org/TR/sparql11-service-description/\#sd-endpoint}
or matched a case-insensitive regular expression \texttt{sparql} if
the subject and objects were both resources, or the predicates
\rdfterm{void:vocabulary}\footnote{http://www.w3.org/TR/void/\#vocabularies},
\rdfterm{rdfa:vocabulary}\footnote{http://www.w3.org/TR/rdfa-core/\#term-prefix-definitions-vocabulary}
or
\rdfterm{api:vocabulary}\footnote{http://purl.org/linked-data/api/vocab\#vocabulary},
as well as having an resource as object. Finally, statements with the
the classes
\rdfterm{cogs:Endpoint}\footnote{http://vocab.deri.ie/cogs\#Endpoint},
\rdfterm{owl:Ontology} and
\rdfterm{voaf:Vocabulary}\footnote{http://lov.okfn.org/vocab/voaf/v2.3/index.html\#Vocabulary}
in the object position were also accepted. More classes and properties
were considered, but not used in the data reduction if they did not
occur in the original data.
